### 2021-05-10 LaTeX-ACM/sections/paper.tex
frontrunning attacks sketch
changes

@@

@@

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata. As the number of pairs increases, L1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,005.

@@

Recall for running functions on \cm on Arbitrum, traders must first instantiate the truncation by sending it to the Arbitrum EthBridge contract. As as soon as this transaction is included in the Layer 1 (Ethereum) block, it will get time-stamped and ordered. Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.

>>>>

%\textblue{Notes on Front-running Table:}
%\begin{itemize}
%\item{Mallory squeezes her order before Alice's.} Mallory sees that there is an incoming bid at 200 for 10 of an asset, and currently, the best offer is at 190 for the same volume. In this case, Mallory sends her bid at 190 for 10 and immediately inserts the sell order at 200. If Alice's transaction gets executed, Mallory will profit on the price difference. 
%\textblue{Sandwich Attacks:} These attacks apply to automated market makers (\ie UniSwap) and exploit a particular feature of AMMs, which is for every swap that takes place on an AMM, the price of the token being swapped shifts slightly. In this case, if Mallory realizes that there is an incoming trade of asset A for asset B, She immediately inserts a bid for asset B. This transaction will increase the price of asset B significantly and when Alice's transaction gets executed on the AMM, she'll receive less number of asset B as she is purchasing it at an inflated price. Right after Alice's transaction goes through, Mallory will sell the amount of asset B she has bought at a higher price.
%\end{itemize}
\input{tables/frontrunning.tex}

@@

% JC: Add option for burning the price improvement, keeping it in Lissy, give it to charity, \etc.

@@

% = = = = = = = = = = = = = = = = = = = = = = = = =  %
\subsection{Token Bridges with Arbitrum}

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). \textblue{On Arbitrum, heaps are XX\% more efficient than non-Heaps for submitting orders and YY\% less efficient for closing.} Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata. As the number of pairs increases, L1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,005.

@@

Recall for running functions on \cm on Arbitrum, traders must first instantiate the truncation by sending it to the Arbitrum EthBridge contract. As as soon as this transaction is included in the Layer 1 (Ethereum) block, it will get time-stamped and ordered. Thus, potential for front-running on Arbitrum is same as those explained in~\ref{sec:front}.'

\textblue{Say something about \texttt{block.coinbase()} and Arbitrum.}
